### 2020-12-11 paper/localpsf.tex
wrote weighting function algorithm at infinite dimensional level

We choose the weighting functions $w_i$ to be the smoothest functions, in a least-squares sense, that interpolate the points $x_i$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid.

@@

In general, product-convolution approximations take the form shown in \eqref{eq:product_convolution}, but $\varphi_i$ and $w_i$ may be arbitrary functions. Product-convolution approximations have been used in a wide variety of fields going back several decades [CITE BIG LIST].
For background on product-convolution approximations, we recommend reading the following papers: [CITES].

@@

In [CITE], Escande and Weiss explored the idea of approximating linear operators from scattered impulse responses using a product-convolution scheme of the same form as \eqref{eq:product_convolution}.

@@

A key advantage of Poisson interpolation over other PSF interpolation methods, most notably radial basis functions [cite Escande etc], is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. Consider the Pine island glacier geometry shown in Figure REF. Regions of the glacier are separated by thin inlets of ocean. With radial basis function interpolation, PSF samples on one side of the inlet inappropriately influence the interpolation on the other side of the inlet. With Poisson interpolation, the PSF samples only influence the interpolation on their own side of the inlet.

>>>>

We choose the weighting functions, $w_i$, to be the solutions to the following optimization problems:
\begin{equation}
\label{eq:wi_optimization_problem_intro}
\begin{aligned}
\min_{w_i} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
\end{aligned}
\end{equation}
Here $\Delta$ is the Laplacian on $\Omega$ with pure Neumann boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. These are the smoothest functions, in a least-squares sense, that interpolate the points $x_i$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation [cite Escande etc], is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. Consider the Pine island glacier geometry shown in Figure REF. Regions of the glacier are separated by thin inlets of ocean. With radial basis function interpolation, points on one side of the inlet inappropriately influence the interpolation on the other side of the inlet. With Poisson interpolation, the PSF samples only influence the interpolation on their own side of the inlet.

@@

In general, product-convolution approximations take the form shown in \eqref{eq:product_convolution}, but $\varphi_i$ and $w_i$ may be arbitrary functions. Product-convolution approximations have been used in a wide variety of fields going back several decades [CITE BIG LIST].
For background on product-convolution approximations, we recommend reading the following papers: [CITES, INCLUDE ESCANDE SCATTERED].

@@

%In [CITE], Escande and Weiss explored the idea of approximating linear operators from scattered impulse responses using a product-convolution scheme of the same form as \eqref{eq:product_convolution}.

@@
